Stimuli List Generation

### 2023-04-24 Stimuli List and Data Source/Stimuli List Generation.Rmd
Updated Stimuli List

file_names <- c("Phrase List 1.xlsx", "Phrase List 2.xlsx")
seed = c(1000, 7036)

@@

  #Merging the practice trials df with the randomized list df
  data_random <- dplyr::full_join(Practice_trials, data_random) %>%
    dplyr::relocate(., targetPhrase, .after = speaker) %>%
    dplyr::relocate(., code, .before = speaker) %>%
    #creating new trial number, block number, and counter balance variables
    dplyr::mutate(., trial = row_number(), 
                  counterBalance = i, 
                  block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1), 
                  practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
    #moving new variables in the data frame
    dplyr::relocate(trial, .before = code) %>%
    dplyr::relocate(block, .before = counterBalance) %>%
    dplyr::relocate(practiceTrial, .after = targetPhrase)

@@

  # Exporting dfs (to create stimuli lists in word)
  rio::export(data_random, paste("New_Phrase_List", i, ".csv", sep = ""))
}

@@

DataSource <- DataSource %>%
  dplyr::mutate(soundFile = case_when(speaker == "Practice" ~ "PM",
                                      speaker == "PD" ~ "PDM10",
                                      TRUE ~ "CM1")) %>%
  dplyr::mutate(soundFile = ifelse(soundFile == "PM", paste(soundFile, trial, sep = "_"), 
                                   paste(soundFile, code, sep = "_"))) %>%
  dplyr::mutate(soundFile = paste(soundFile, "wav", sep = ".")) %>%
  dplyr::mutate(num_targetWords = ifelse(code == "EXP_18" | code == "EXP_75", 2, 3)) %>%
  dplyr::relocate(soundFile, .before = targetPhrase) %>%
  dplyr::relocate(num_targetWords, .before = block)

@@

rio::export(DataSource, "Dysarthria_LE_DataSource.csv")

>>>>

file_names <- c("Phrase lists/Phrase List 1.xlsx", "Phrase lists/Phrase List 2.xlsx")
seed = c(1000, 7036)

@@

  #Merging the practice trials df with the randomized list df
  data_random <- dplyr::full_join(Practice_trials, data_random) %>%
    dplyr::relocate(., targetPhrase, .after = speaker) %>%
    dplyr::relocate(., code, .before = speaker) %>%
    #creating new trial number, block number, and counter balance variables
    dplyr::mutate(., trial = row_number(), 
                  counterBalance = i, 
                  block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1), 
                  practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
    # Changing PD speaker to ALS speaker (we decided to use a different speaker for this study)
    dplyr::mutate(speaker = case_when(speaker == "PD" ~ "ALS",
                                      TRUE ~ speaker)) %>%
    #moving new variables in the data frame
    dplyr::relocate(trial, .before = code) %>%
    dplyr::relocate(block, .before = counterBalance) %>%
    dplyr::relocate(practiceTrial, .after = targetPhrase)

@@

}

@@

DataSource <- DataSource %>%
  dplyr::mutate(soundFile = case_when(speaker == "Practice" ~ "PM",
                                      speaker == "ALS" ~ "ALSM1",
                                      TRUE ~ "CM1")) %>%
  dplyr::mutate(soundFile = ifelse(soundFile == "PM", paste(soundFile, trial, sep = "_"), 
                                   paste(soundFile, code, sep = "_"))) %>%
  dplyr::mutate(soundFile = paste(soundFile, "wav", sep = ".")) %>%
  dplyr::relocate(soundFile, .before = targetPhrase)

@@

rio::export(DataSource, "Data Source/Dysarthria_LE_DataSource.csv")
